Models of VOR learning in MHC knockout mice

### 2013-02-14 Notes/VORmodel.tex
redesigned figure captions

\newcommand{\resultsfig}[2]{\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{#1_learn.eps}}\label{fig:#1_learn}
  \item\aligntop{\includegraphics[width=7cm]{#1_learnS.eps}}\label{fig:#1_learnS}
  \item\label{fig:#1_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{#1_eq_WT.eps}}\label{fig:#1_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{#1_eq_KO.eps}}\label{fig:#1_eq_KO}
                  \end{myenumi}
  \item\label{fig:#1_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_WT_nopre.eps}}\label{fig:#1_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_WT_pre.eps}}\label{fig:#1_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_KO_nopre.eps}}\label{fig:#1_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_KO_pre.eps}}\label{fig:#1_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption[#2]{#2.
  Other parameters can be found in \autoref{tr:#1} of \autoref{tab:params}.
  Time is measured in units of $1/r$, the mean time between plasticity events.
  (\ref{fig:#1_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:#1_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:#1_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:#1_eq_WT}) wild-type and (\ref{fig:#1_eq_KO}) \KO\ mutant,
  with states of weak synaptic strength to the left and strong states to the right.
  (\ref{fig:#1_pr}) Evolution of probability distributions for (\ref{fig:#1_pr_WT_nopre}\ref{fig:#1_pr_WT_pre}) wild-type and  (\ref{fig:#1_pr_KO_nopre}\ref{fig:#1_pr_KO_pre}) \KO\ mutant without (\ref{fig:#1_pr_WT_nopre},\ref{fig:#1_pr_KO_nopre}) and with (\ref{fig:#1_pr_WT_pre},\ref{fig:#1_pr_KO_pre}) pre-training,
  with states of weak synaptic strength at the top and strong states underneath. } \label{fig:#1}
\end{figure}}

@@

\resultsfig{cascade_short}{Simulation results for the cascade model with short pre-training ($rt_\text{pre}=50$)}

\resultsfig{cascade_long}{Simulation results for the cascade model with long pre-training ($rt_\text{pre}=150$)}

@@

\resultsfig{multistate_weak}{Simulation results for the multistate model with weak training ($\Delta f=-0.1$)}

\resultsfig{multistate_med}{Simulation results for the multistate model with moderate training ($\Delta f=-0.17$)}

\resultsfig{multistate_strong}{Simulation results for the multistate model with strong training ($\Delta f=-0.4$)}

@@

\resultsfig{multistate_lin}{Simulation results for multistate model with linear weights}%\label{fig:multistate_lin}

@@

\resultsfig{binary}{Simulation results for two-state model}

@@

\resultsfig{pooled_plenty}{Simulation results for the pooled resource model with light depletion ($q\lmin/q\lmax=0.75$)}

\resultsfig{pooled_scarce}{Simulation results for the pooled resource model with heavy depletion ($q\lmin/q\lmax=0.25$)}

>>>>

\newcommand{\resultsfig}[3]{\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{#3_learn.eps}}\label{fig:#3_learn}
  \item\aligntop{\includegraphics[width=7cm]{#3_learnS.eps}}\label{fig:#3_learnS}
  \item\label{fig:#3_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{#3_eq_WT.eps}}\label{fig:#3_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{#3_eq_KO.eps}}\label{fig:#3_eq_KO}
                  \end{myenumi}
  \item\label{fig:#3_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{#3_pr_WT_nopre.eps}}\label{fig:#3_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{#3_pr_WT_pre.eps}}\label{fig:#3_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{#3_pr_KO_nopre.eps}}\label{fig:#3_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{#3_pr_KO_pre.eps}}\label{fig:#3_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption[#1]{#1 #2.
  Other parameters can be found in \autoref{tr:#3} of \autoref{tab:params}.
  Time is measured in units of $1/r$, the mean time between plasticity events.
  (\ref{fig:#3_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:#3_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:#3_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:#3_eq_WT}) wild-type and (\ref{fig:#3_eq_KO}) \KO\ mutant,
  with states of weak synaptic strength to the left and strong states to the right.
  (\ref{fig:#3_pr}) Evolution of probability distributions for (\ref{fig:#3_pr_WT_nopre}\ref{fig:#3_pr_WT_pre}) wild-type and  (\ref{fig:#3_pr_KO_nopre}\ref{fig:#3_pr_KO_pre}) \KO\ mutant without (\ref{fig:#3_pr_WT_nopre},\ref{fig:#3_pr_KO_nopre}) and with (\ref{fig:#3_pr_WT_pre},\ref{fig:#3_pr_KO_pre}) pre-training,
  with states of weak synaptic strength at the top and strong states underneath. } \label{fig:#3}
\end{figure}}

\newcommand{\resultsfign}[2]{\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{#2_learn.eps}}\label{fig:#2_learn}
  \item\aligntop{\includegraphics[width=7cm]{#2_learnS.eps}}\label{fig:#2_learnS}
  \item\label{fig:#2_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{#2_eq_WT.eps}}\label{fig:#2_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{#2_eq_KO.eps}}\label{fig:#2_eq_KO}
                  \end{myenumi}
  \item\label{fig:#2_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{#2_pr_WT_nopre.eps}}\label{fig:#2_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{#2_pr_WT_pre.eps}}\label{fig:#2_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{#2_pr_KO_nopre.eps}}\label{fig:#2_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{#2_pr_KO_pre.eps}}\label{fig:#2_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption[#1]{#1.
  Parameters can be found in \autoref{tr:#2} of \autoref{tab:params}.
  Time is measured in units of $1/r$, the mean time between plasticity events.
  (\ref{fig:#2_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:#2_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:#2_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:#2_eq_WT}) wild-type and (\ref{fig:#2_eq_KO}) \KO\ mutant,
  with states of weak synaptic strength to the left and strong states to the right.
  (\ref{fig:#2_pr}) Evolution of probability distributions for (\ref{fig:#2_pr_WT_nopre}\ref{fig:#2_pr_WT_pre}) wild-type and  (\ref{fig:#2_pr_KO_nopre}\ref{fig:#2_pr_KO_pre}) \KO\ mutant without (\ref{fig:#2_pr_WT_nopre},\ref{fig:#2_pr_KO_nopre}) and with (\ref{fig:#2_pr_WT_pre},\ref{fig:#2_pr_KO_pre}) pre-training,
  with states of weak synaptic strength at the top and strong states underneath. } \label{fig:#2}
\end{figure}}

@@

\resultsfig{Simulation results for the cascade model with short pre-training}{($rt_\text{pre}=50$)}{cascade_short}

\resultsfig{Simulation results for the cascade model with long pre-training}{($rt_\text{pre}=150$)}{cascade_long}

@@

\resultsfig{Simulation results for the multistate model with weak training}{($\Delta f=-0.1$)}{multistate_weak}

\resultsfig{Simulation results for the multistate model with moderate training}{($\Delta f=-0.17$)}{multistate_med}

\resultsfig{Simulation results for the multistate model with strong training}{($\Delta f=-0.4$)}{multistate_strong}

@@

\resultsfign{Simulation results for multistate model with linear weights}{multistate_lin}

@@

\resultsfign{Simulation results for two-state model}{binary}

@@

\resultsfig{Simulation results for the pooled resource model with light depletion}{($q\lmin/q\lmax=0.75$)}{pooled_plenty}

\resultsfig{Simulation results for the pooled resource model with heavy depletion}{($q\lmin/q\lmax=0.25$)}{pooled_scarce}
